---
title: "Abu Dhabi Tourist Destinations"
author: "jsuk"
date: "12/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

I would like to introduce some tourist destinations in my current place of residence - Abu Dhabi, United Arab Emirates.
To effectively show the places, I will make a simple interactive map using 'leaflet' package in R.

The attractions that I would like to represent on a map includes: <br>
Sheikh Zayed Grand Mosque, Emirates Palace, Ferrari World, Louvre, Qasr AlHosn, Marina Circuit,
Qasr Alwatan, Mangrove National Park.

The places will be marked on a map with coordinates, small icon images and pop ups (website links and one-line description.

---

## Create a map

```{r, echo=FALSE, comment="", message=FALSE}
library(leaflet); library(dplyr);
```

```{r, echo=FALSE}
# Prepare data for places

ad_places = data.frame(
  name = c('Qasr Al Watan', 'Emirates Palace', 'Qasr AlHosn', 'Sheikh Zayed Grand Mosque', 
           'Mangrove National Park', 'Louvre', 'Ferrari World', 'Marina Circuit'),
  lat = c(24.4627203,24.4616485,24.4822419,24.4128383,24.4560699,24.5337003,24.4835529,24.4699462),
  lng = c(54.3035231,54.3150946,54.3525343,54.4727867,54.4156119,54.3959481,54.6029024,54.603318)
)

```

```{r, echo=FALSE, comment=""}
# Create icon set

icon_urls = c('https://encrypted-tbn2.gstatic.com/licensed-image?q=tbn:ANd9GcQa0QD_4_PepH0ieOtU8ZmNa_IBtIOIUeScek-cn5ovN-bDRuDRe6-n_XOwo0hWvtZfB6KNY4GjAQ4EMWEmmuYs4A',
              'https://encrypted-tbn2.gstatic.com/images?q=tbn:ANd9GcSXEB3HjikNzvVUrVXUThme9Z2ifP-Z7axRaXjJF_vJPW3if4zAVnnimrRPEm9HIYUzILfiIaqxgGskJp3AQqgIfQ',
              'https://encrypted-tbn3.gstatic.com/images?q=tbn:ANd9GcS5AXcMn8bxfHKH6GHb-HvpDi5Wf2PibF-gaEU-QxqSDN3O_YfaW3WlGP7iFILpl2hm8OeE6--8X2S2BXriG35FXw',
              'https://encrypted-tbn0.gstatic.com/licensed-image?q=tbn:ANd9GcTMGB-l_RoCvjF50Fw9Akw2QGA0Rrcsr_P_wLYsn8lbfQXfC4UHYWWpXf6MbImvMFP9A-6W2glMnqSOP8xJxQPaKA',
              'https://encrypted-tbn2.gstatic.com/images?q=tbn:ANd9GcSmvOcNZFNZSJeZmPDJTvr63OFyW10sQE4HEwuX6pUr_h5YXNml90q_oN5If-1TZtKZwoTfMdcHSTCBq2gZr9h7Og',
              'https://encrypted-tbn2.gstatic.com/images?q=tbn:ANd9GcSk0_iNHBFa5tGQ6JWO5TAg6wXj6955CVd-cDh9rzasPPn7SMNUy2yjBjwl0yEFN7kUmHauxte3PgqrfvQrmoLeKg',
              'https://encrypted-tbn3.gstatic.com/images?q=tbn:ANd9GcQsx2RKxKzDSbCEOR4h8t4Xug8EhSeAWqmttHPoDFZjo0XJ2awMttolW8wJkj11cAm8scqTmIDzTABQB1THOzuraw',
              'https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcT2ydFFOqEXGDRfatJsPNFBlScOH0WV6Iompt6qIc-UbBqvP1leE5tSku_RYgnR18wtLTi7sZrH8q7ojLYnT7_ALA'
)


icon_set = iconList(
  m1 = makeIcon(icon_urls[1], iconWidth=64, iconHeight=64),
  m2 = makeIcon(icon_urls[2], iconWidth=64, iconHeight=64),
  m3 = makeIcon(icon_urls[3], iconWidth=64, iconHeight=64),
  m4 = makeIcon(icon_urls[4], iconWidth=64, iconHeight=64),
  m5 = makeIcon(icon_urls[5], iconWidth=64, iconHeight=64),
  m6 = makeIcon(icon_urls[6], iconWidth=64, iconHeight=64),
  m7 = makeIcon(icon_urls[7], iconWidth=64, iconHeight=64),
  m8 = makeIcon(icon_urls[8], iconWidth=64, iconHeight=64)
)

```

```{r, echo=FALSE, comment=""}
# Create pop ups

ad_popups= c(
  "<a href='https://www.qasralwatan.ae/en/'>Qasr Al Watan</a><br><span>Marble & limestone presidental palace</span>",
  "<a href='https://www.mandarinoriental.com/abu-dhabi/emirates-palace/luxury-hotel'>Emirates Palace</a><br><span>Palatial hotel with a private marina</span>",
  "<a href='https://qasralhosn.ae/'>Qasr AlHosn</a><br><span>Landmark 18th-century palace & fort</span>",
  "<a href='https://www.szgmc.gov.ae/en/'>Sheikh Zayed Grand Mosque</a><br><span>Iconic landmark with 82 white domes</span>",
  "<a href='https://park.jubailisland.ae/'>Mangrove with many birds and watersports/a>",
  "<a href='https://www.louvreabudhabi.ae/'>Louvre Abu Dhabi</a><br><span>Unique museum for international artwork</span>",
  "<a href='http://www.ferrariworldabudhabi.com'>Ferrari World</a><br><span>M<otorsport-themed entertainment complex</span>",
  "<a href='https://www.yasmarinacircuit.com/en/g'>Marina Circuit</a><br><span>Formula 1, auto racing and marina</span>"
)

```

```{r fig.alt="Abu Dhabi Tourist Destination Map", out.width="100%"}
# Create interactive plots 
# with data and attributes constructed above

ad_places %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(lat=ad_places$lat, lng=ad_places$lng, icon = icon_set, popup = ad_popups, 
             clusterOptions = markerClusterOptions()) %>% 
  addCircles(lat=ad_places$lat, lng=ad_places$lng)

```


---

## Acknowledgement

Each information are retrieved from:

- Descriptions, website Links and image urls:  [Google Things To Do](https://bit.ly/3lWXOKo)
- Coordinates: Google Maps

